How to Avoid OOTA Without Really Trying

### 2024-10-02 paper/ootavacuous.tex
ootavacuous: Make first sentence of 7.1 more explicit
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Section 7.2 header s/versus/vs./
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as wishy-washy and avoiding the real
problem, in that a given piece of code should either contain or not
contain a semantic dependency, independent of the implementation used to
run it.

@@

\subsection{Global Analysis and Volatile versus Quasi Volatile}
\label{sec:Global Analysis and Volatile versus Quasi Volatile}

>>>>

One drawback of our definition of semantic dependency is that it is only
relative to a specific compiler or implementation.
This may strike some people as wishy-washy and avoiding the real
problem, in that a given piece of code should either contain or not
contain a semantic dependency, independent of the implementation used to
run it.

@@

\subsection{Global Analysis and Volatile vs.\ Quasi Volatile}
\label{sec:Global Analysis and Volatile vs. Quasi Volatile}
